\documentclass[11pt]{article}
\usepackage[a4paper,margin=2.8cm]{geometry}
\usepackage{amsfonts}


\usepackage{mathtools}
\usepackage{cancel}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage[dvipsnames,usenames]{color}
\usepackage[colorlinks=true,linkcolor=NavyBlue,citecolor=NavyBlue,urlcolor=NavyBlue]{hyperref} % for hyperlinks 

% makros 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\R}{\mathds {R}}
\newcommand{\red}[1]{\textcolor{red}{#1}} % for color for remarks


\title{Cournot Competition with Idiosyncratic Taxation}

\author{Nate Dwyer and Sandro Lera}

\begin{document}

\maketitle
\setcounter{section}{0}
\section{Model Definition}
We simulate an economy of buyers and sellers as an extension of the Cournot competition model, 
with additional buyer-seller specific (`idiosyncratic') transaction cost (`tax'). 
The goal of this tax is to avoid market dominance by one single seller based on initially only small differences in quality. 
Instead, the model is aimed at striking a `fair' balance between market competition and seller protection. 

The `geography' of our model is one-dimensional with periodic boundaries, i.e. a topological circle, of length $L$. 
Due to the periodic boundary conditions, we measure physical distances with the metric $\min(|x-y|, L-|y-x|)$ for any two points (`agents') $x$,$y$ on $L$. 
Without loss of generality, we set $L=1$. 
Our model does not rely on the implemented geography, and any other, potentially more realistic topology could be considered. 

\subsection{Buyers}
On that circle we place some $|B|$ buyers randomly distributed. The buyers all
have an identical demand curve $Q+P = a$, and each buyer $b\in B$ buys a quantity
$\vec{b}$, where $b_i$ is the amount $b$ buys from the $i$th seller. Each buyer
tries to buy as much total quantity as they can while keeping $P + Q < a$ i.e.
they try to maximize $\sum_{i=0}^{|S|}b_i$. 

\subsection{Sellers}
On that circle we will also find some $|S|$ sellers, who all offer the same
product, but at potentially different prices and in potentially different
quantities. We denote the prices that are offered by a vector $\vec{p}$ and the
quantities by the vector $\vec{q}$, where the $i$th seller offers $q_i$ amount
of the product at a price $p_i$. Each seller chooses $q_i$ and $p_i$
simultaneously in an attempt to maximize profit.  

\subsection{Idiosyncratic tax}
For any buyer $b$ and seller $s$, we define a product-distance $D = D(b,s)$ such
that the seller s that is physically closest to b has distance $D(b,s)=1$, the
next closest has distance $D=2$, and so on. 

If buyer b buys from seller s, the total price, including transaction cost
(tax), is given by $p(b,s) = p_s  \cdot D(b,s)^\gamma$ where $\gamma$ is a scaling
coefficient. 

\subsection{Profit Function}

The profit function for seller $i$ reads
\begin{equation}
    \Pi_i = p_iq_i^s - cq_i, 
    \label{eq:profit_function}
\end{equation}
where $c$ is the price to produce each unit of product, and $q_i^s$ is the quantity the $i$th seller sells
(which may be less but never more than the quantity $q_i$ that was produced). 
Below, we then introduce the profit vector $\vec{\pi} = (\pi_1, \ldots, \pi_{|S|})$
to find the Nash-equilibrium based on the profit functions of all sellers.


\section{Mathematical Representation}
We construct a set of buyers $B$ and a set of sellers $S$, and transaction cost
function $t: (B\times S)\rightarrow \R$, which has subfunctions $t_b:
S\rightarrow \R$ s.t. for all $s\in S$, $t(b,s) = t_b(s)$.
\red{
I don't see what are these sub-functions for. 
The way I see it, a specific customer-seller tax is a mapping from $B \times S$ to $\R$.
There is no subfunction.}

Also, we construct an demand curve for all $b\in B$, namely $P = a - Q$.

\section{Function to put into Gambit}

We construct a function $\Pi : (\R\times\R)^{|S|} \rightarrow \R^{|S|}$ s.t.
$\Pi(\vec{s}) = \vec{\pi}$, where the elements of $\vec{s}$ are the tuples
$(q_i,p_i)$ listing the quantity produced and the price offered by the $i$th
seller, and the elements of $\vec{\pi}$ are $\pi_i$, the profits of the $i$th
seller. \red{Write from seller $s$, here and everywhere else.}

Given $\vec{s}$, $\vec{\pi}$ is calculated by first calculating $\vec{q}^s$, the
vector of total quantity sold, then using it to calculate $\vec{\pi}$ using 
equation \eqref{eq:profit_function}.  

\red{(don't start a sentence like that)}
$q^s_i = \sum _{b\in B} b_i$, where $b_i$ is the amount seller $b$ buys from the
$i$th seller.  
\red{Turn that thing into vectorial notation. You have two matrices, $Q$ and $Q^s$, and the same for prices. Then you have $Q_{sb}$ instead of $Q_{ji}$}

Each buyer $b$ chooses a vector $\vec{b}$, where each element
$b_i$ is the amount $b$ bought from the $i$th buyer.  

Set $\vec{q}^{unsold} = \vec{q}$

For each $b_i \in \vec{b}$, have it maximize the total quantity bought by $b$
while remaining under the individual demand curve $P=a-Q$.  The resulting vector
that lists the amount $b$ buys from each seller is $\vec{b}$.  Subtract
$\vec{b}$ from $\vec{q}^{unsold}$ to get a new $\vec{q}^{unsold}$.

\subsection{Algorithm to determining what a buyer purchases}
To determine $\vec{b}$, do the following:
\red{Use a proper enumeration environment}

\begin{enumerate}
	\item bla 
	\item bla 
\end{enumerate}

Calculate $b$'s perceived prices, $t_b(s_i) * p_i = \vec{p}^b$, then turn it
into a $|S|$ by 2 matrix $M$ with the first column being the price, $\vec{p}$
the second column being the remaining quantity, $\vec{q}^{unsold}$. 

Sort $M$'s rows by the perceived price column, and re-index the rows\newline $0,
1, \cdots , j, \cdots , |S|$. 

Find the maximal index $j$ and quantity $q^{*}_j \le q^{unsold}_j$ such that
$p_j + q^{*}_j + \sum_{k=0}^j q_k \le a$.  Now we have a vector of amount bought
by $b$ as follows: $<q_0, q_1,\cdots q_{j-1}, q^{*}_j, 0, 0, \cdots, 0>.$

Finally, re-index this new vector using the $i$-index instead of the $j$ index
to get $\vec{b}$.

\section{Open Questions}

\begin{itemize}

	\item With this model, we want to demonstrate that initially small differences in quality do not lead to proportional feedback
		mechanisms that lead to an unequal output distribution
		So it might be questionable if the current Cournot model is the model of our interests, 
		because it assumes all buyers set the same price. 

\end{itemize}

\end{document}
